New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-07-26 paper/answer_rev_2.tex
wip

		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.
		\href{http://www.sharelatex.com}{Something Linky}

>>>>

		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.

		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint. That is, there is a non-overlapping solution, however, none of them is in the set of solutions we look for.
